Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-07-06 TEBenchmarkPaper/article.tex
TEB: Remove unused cruft
TEB: Mention Nix, give link to TE overview page and github

% For interestingness table
\newcommand{\iE}{\textbf{E}}
\newcommand{\iN}{\textbf{N}}
\newcommand{\iS}{\textbf{S}}
\newcommand{\iA}{\textbf{A}}
\newcommand{\iC}{\textbf{C}}
\newcommand{\iU}{\textbf{U}}
\newcommand{\tIFF}{if-and-only-if}
\newcommand{\tNE}{non-exists}
\newcommand{\tIMP}{implies}
\newcommand{\tEQ}{equations}
\newcommand{\tINE}{inequalities}
\newcommand{\tCON}{conditional}
\newcommand{\tRow}[1]{#1 \\ \hline}

@@

% Look carefully at each tool's (paper's) eval section

% Make it clear that methodology is the point (it's not just a detail, like in a
% chemistry paper for example)

@@

% Lay out the field of TE: motivation, tools, evaluation, problems...

@@

\begin{sloppypar}
  Our benchmark, including the scripts used to generate it from the TIP problem
  set, is available online at
  \url{https://github.com/warbo/theory-exploration-benchmarks}. The application
  to QuickSpec is at \url{https://github.com/warbo/haskell-te} and IsaCoSy at
  \url{https://github.com/warbo/isaplanner-tip}.
\end{sloppypar}

%- Existing approaches are difficult to compare
% - They want different things
% - They're evaluated differently
% - They're evaluated ``locally'' (as white boxen)

% Look at phd symposium 2017, moa's conjecture synthesis paper, etc.
% We can just jump straight in to automated conjecture generation

@@

% more detail about evaluation, interestingness, etc. Reference Simon/Alan
% interestingness, e.g. examples from textbooks, etc.

>>>>

@@

@@

@@

\begin{sloppypar}
  Our benchmark implementation is available at
  \url{http://chriswarbo.net/projects/theory-exploration} and
  \url{https://github.com/warbo}. All processes, including benchmark generation,
  experimental runs and generation of this paper, are specified using the
  Nix~\cite{dolstra2004nix} system to aid reproducibility.
\end{sloppypar}

@@
